Relative parabolic factorizations of Chevalley groups

### 2015-09-10 dennis-vaserstein.tex
Minor changes

\begin{lemma}\label{lemma:Stein_reduction}
Assume that there exists a subset $B \subseteq \E(\Delta_r, R, I)$ satisfying the following assumptions:
\begin{enumerate}
 \item\label{stein_cond1} One has $\U(\Sigma^+_r, I)\cdot \U(\Sigma^-_r, I) \cdot \E(\Delta_r, R, I) \subseteq \U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot B.$
 \item\label{stein_cond2} One has $X_{-\alpha\ssub{r}}(I)^B \subseteq \EP_s(R, I).$
\end{enumerate}
Then $X_{-\alpha_r}(R) \subseteq N_{rs}.$
\end{lemma}
\begin{proof}
Set $A:=\U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot B \cdot \EP_s(R, I).$
From the first assumption of the lemma it follows that $A_{rs}=A$.
On the other hand, by the second assumption we have
\begin{multline*}
X_{\alpha_r}(I) \cdot X_{-\alpha_r}(I) \cdot B \cdot \EP_s(R, I) \subseteq 
X_{\alpha_r}(I) \cdot B \cdot \EP_s(R, I) \cdot \EP_s(R, I) \subseteq \\
\subseteq B \cdot \U(\Sigma_r, I) \cdot \EP_s(R, I) =
B \cdot \EP_s(R, I).
\end{multline*}
Together with the third statement of~\cref{lemma:dv_unipotent} this implies that
\begin{equation*} \label{rel:sred}
A = \U(\Phi^+\setminus\{\alpha_r\}, I) \cdot \U(\Phi^-, I) \cdot B \cdot \EP_s(R, I).
\end{equation*}
Consequently, since $[B, X_{-\alpha_r}(R)] \subseteq \U(\Sigma_r^-, R) \cap \E(\Phi, R, I) = \U(\Sigma_r^-, I)$ we get that:
\begin{equation*} \label{rel:ninv} A^{X_{-\alpha\ssub{r}}(R)} = \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot B ^{X_{-\alpha\ssub{r}}(R)} \cdot \EP_s(R, I) = A, \end{equation*}
which implies the assertion of the lemma. \end{proof}

@@

Yet another advantage of weight diagrams is that they allow one to visualize the action of elementary root unipotents $x_\alpha(\xi)$ on $v = \sum_{\lambda \in \Lambda(\pi)} v_\lambda e_\lambda \in V$ described in~\cref{lemma:Matsumoto}.
Such description for microweight $\pi$ and $\alpha = \pm\alpha_i\in \pm\Pi$ is particularly simple: 
for every bond of the diagram joining vertices $\lambda$ and $\lambda + \alpha$ the element $x_{\alpha}(\xi)$ adds $\pm \xi \cdot v_\lambda$ to $v_{\lambda+\alpha}$.
See~\cite[Section~3.4]{PSV98} for more detailed description.

\begin{figure}
\[\begin{array}{l @{\qquad} l @{\qquad} c @{\quad} c @{\qquad} l @{\qquad} l}
\Phi                                 & (s,r)         & |\Lambda(\pi)| & \text{type of $\pi$} & |\Lambda(\pi')|& |\Gamma|  \\ \hline\vphantom{\Bigl(}
\rA_\ell,\ \ell\geqslant 2           & (1,\ell)      & \ell+1         & \text{natural}       & \ell           & 1  \\     
\rB_\ell,\ \ell\geqslant 2           & (1,\ell)      & 2\ell+1        & \text{natural}       & \ell           & 1  \\     
\rC_\ell,\ \ell\geqslant 2           & (1,\ell)      & 2\ell          & \text{natural}       & \ell           & 1  \\
\rD_\ell,\ \ell\geqslant 4           & (1,\ell)      & 2\ell          & \text{natural}       & \ell           & 2  \\ 
\rD_\ell,\ \ell\geqslant 4           & (\ell,\ell-1) & 2^{\ell-1}     & \text{half-spinor}   & \ell           & \ell-2  \\
\rE_\ell,\ \ell=6,7                  & (\ell,2)      & 27, 56         & \text{minimal}       & \ell           & 3       \\ 
\rE_\ell,\ \ell=6,7                  & (\ell,1)      & 27, 56         & \text{minimal}       & 2(\ell-1)      & \ell-1  \end{array}\]
 \caption[Table]{List of representation involved in the proof of~\cref{thm:DennisVaserstein}.} \label{fig:table}
\end{figure}

Now let $B$ be the set of all elements $g$ of $\E(\Delta_r,R, I)$ such that $(g \cdot v^+)_\lambda = 0$ for all $\lambda\in\Gamma$.
Applying~\cref{lemma:uraction} to the subsystem $\Delta_r$ we find
$x\in\U(\Delta_r^+, I)$, $y\in \U(\Delta_r^-, I)$ such that $yx\cdot g \in B$.
This proves the first assumption of~\cref{lemma:Stein_reduction}, indeed:
\[ \U(\Sigma^+_r, I) \cdot \U(\Sigma^-_r, I) \cdot g = \U(\Sigma^+_r, I) x^{-1} \cdot \U(\Sigma^-_r, I)^{x^{-1}} y^{-1} (yxg) \subseteq \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot B. \]
To prove the second assumption of~\cref{lemma:Stein_reduction} notice that by~\cref{lemma:Matsumoto} and the definition of $\Gamma$ for any $s\in I$, $ g\in B$ one has $x_{-\alpha_r}(s) \cdot g \cdot v^+ = g \cdot v^+$ hence
\[ X_{-\alpha\ssub{r}}(I)^{B} \subseteq \U(\Phi^-, I) \cap \Stab(v^+) \subseteq \U(\Delta_s^-, I) \subseteq \EP_s(R, I). \]

\begin{proof}[Proof of~\cref{thm:DennisVaserstein}]
By the above discussion we may assume that the assertion of~\cref{lemma:Stein_reduction} holds.
Set $\Pi' = \Pi \setminus \{\alpha_s\}$.
From~\cref{lemma:dv-normal} and \cref{lemma:Stein_reduction} it follows that $X_\alpha(R) \subseteq N_{rs}$ for $\alpha \in \Pi' \cup -\Pi'$.
Since $\Delta_s$ is irreducible we get from~\cref{item-egen} that $\E(\Delta_s, R) \subseteq N_{rs}$.

Our next step is to show that $\U(\Sigma_s, R) \subseteq N_{rs}$.
First of all, notice that by~\cref{lemma:dv-normal} we have the inclusion $X_{\alpha_s}(R) \subseteq N_{rs}$.
In all cases under consideration except $\Phi=\rC_\ell$ we have $m_s(\alpha_{\mathrm{max}})=1$.
Therefore, for $\Phi\neq \rB_\ell, \rC_\ell$ all the roots of $\Sigma^+_s$ have the same $s$-shape and length and the assertion follows from~\cref{item-trans2}.

@@

We defer the proof in the case $\Phi=\rC_\ell$ until we prove~\cref{lemma:DVcaseCl} below.

Our ultimate goal is to show the inclusion $\E(\Phi, R, I) \subseteq L_{rs}$. 
By~\cref{prop:Stepanov} it is enough to prove that $\mathcal{Z}(\Sigma^-_s) \subseteq L_{rs}$.
In view of formula~\eqref{rel:NnormL} and the previous part of the proof it suffices to show only that $\mathcal{X} \subseteq L_{rs}$.
It is clear that $\EP_r(R, I) \subseteq L_{rs}$.
Since $\EP_s(R, I) \subseteq \EP_s(R) \subseteq N_{rs}$ we also conclude that $\EP_s(R, I) \subseteq L_{rs}$, indeed, for $g \in \EP_s(R,I)$ one has
\[ g \cdot A_{rs} \subseteq g \cdot {A_{rs}}^g = A_{rs} \cdot g = A_{rs}. \]
Thus, we are left to prove the inclusion $\U(\Sigma^-_r \cap \Sigma^-_s, I) \subseteq L_{rs}$.

Just as in the above argument all the cases except $\Phi = \rB_\ell, \rC_\ell$ follow from~\cref{item-trans2}.
In the case $\Phi=\rB_\ell$ from $x_{0, 1}(-a) = [x_{2,1}(-a), x_{0, 2}(-1)]\cdot x_{-2,1}(a)$ we conclude that
$$X_{0,1}(I) \subseteq X_{2,1}(I) \cdot X_{2,1}(I)^{x_{0,2}(1)} \cdot X_{-2,1}(I) \subseteq L_{rs} \cdot L_{rs}^{N_{rs}} \cdot L_{rs} \subseteq L_{rs},$$
whence the statement of the theorem follows. \end{proof}

@@

By~\cref{item:asrUnipC} (applied to the subgroup $\G(\Delta_1, R, I)$) we find for every $g \in \EP_1(R, I)$ a matrix $x \in \U(\Sigma_\ell \cap \Delta_1, I)$ such that $xg \in C$.  
Notice that one immediately gets the equality $A_{\ell, 1} = A'$ from this.
Indeed for $g\in \EP_1(R, I)$ one has
\begin{equation*} \EP_\ell(R, I) \cdot \U(\Sigma_1^- \cap \Sigma_\ell^-, I) \cdot g \subseteq 
 \EP_\ell(R, I)x^{-1}  \cdot \U(\Sigma_1^-, I) \cdot xg \subseteq A'. \end{equation*}

By the very definition of $C$, for every $g \in C$ one can choose $y \in \U(\Sigma_1 \cap \Delta_\ell, I)$ such that $(y \cdot g)_{1,2} = 0$.
Consequently, for every $g\in C$ one has
\begin{multline*}
 \EP_\ell(R, I) \cdot \U(\Sigma_1^- \cap \Sigma_\ell^-, I) \cdot g \subseteq \EP_\ell(R, I) y^{-1} \cdot \U(\Sigma_\ell^-\cap \Sigma_1^-, I)^{y^{-1}} \cdot y g \subseteq \\
  \subseteq \EP_\ell(R, I) \cdot \U(\Sigma_\ell^-, I) \cdot y g
\end{multline*}
Direct calculation using~\cref{lemma:Chevalley-Matsumoto} shows that $(yg)^{x_{2,1}(\xi)} = u h$ for $\xi \in R$, $u \in \U(\Sigma_1^-, I)$, $h \in \EP_1(R, I)$ hence
\begin{multline*} {A_{\ell,1}}^{X_{-\alpha_1}(R)} = A'^{X_{2,1}(R)} \subseteq \EP_\ell(R, I)^{X_{2,1}(R)} \cdot \U(\Sigma_\ell^-, I)^{X_{2,1}(R)} \cdot \U(\Sigma_1^-, I) \cdot \EP_1(R, I) \subseteq \\
 \subseteq \EP_\ell(R, I) \cdot \U(\Phi^-, I) \cdot \EP_1(R, I) \subseteq A_{\ell,1} \end{multline*}
 as claimed.
\end{proof}

\begin{proof}[End of the proof of~\cref{thm:DennisVaserstein}]
In the remaining case $\Phi=\rC_\ell$ we conclude from~\cref{lemma:dv-normal,lemma:Stein_reduction,lemma:DVcaseCl} that $X_{\pm \alpha_i}(R) \subseteq N_{\ell,1}$, $1\leq i\leq \ell$.
Therefore, by~\cref{lemma:weylfacts} we get that $\widetilde{W}(\Phi) \subseteq N_{\ell,1}$ and hence $\mathcal{X} \subseteq L_{\ell,1}$ as required.
\end{proof}

>>>>

\begin{lemma}\label{lemma:Stein_reduction}
Assume that there exists a subset $B \subseteq \E(\Delta_r, R, I)$ satisfying the following assumptions:
\begin{enumerate}
 \item\label{stein_cond1} One has $\U(\Sigma^+_r, I)\cdot \U(\Sigma^-_r, I) \cdot \E(\Delta_r, R, I) \subseteq \U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot B.$
 \item\label{stein_cond2} One has $X_{-\alpha\ssub{r}}(I)^B \subseteq \EP_s(R, I).$
\end{enumerate}
Then $X_{-\alpha_r}(R) \subseteq N_{rs}.$
\end{lemma}
\begin{proof}
Set $A:=\U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot B \cdot \EP_s(R, I).$
From the first assumption of the lemma it follows that $A_{rs}=A$.
On the other hand, by the second assumption we have
\begin{multline*}
X_{\alpha_r}(I) \cdot X_{-\alpha_r}(I) \cdot B \cdot \EP_s(R, I) \subseteq 
X_{\alpha_r}(I) \cdot B \cdot \EP_s(R, I) \cdot \EP_s(R, I) \subseteq \\
\subseteq B \cdot \U(\Sigma_r, I) \cdot \EP_s(R, I) =
B \cdot \EP_s(R, I).
\end{multline*}
Together with the third statement of \cref{lemma:dv_unipotent} this implies that
\begin{equation*} \label{rel:sred}
A = \U(\Phi^+\setminus\{\alpha_r\}, I) \cdot \U(\Phi^-, I) \cdot B \cdot \EP_s(R, I).
\end{equation*}
Consequently, since $[B, X_{-\alpha_r}(R)] \subseteq \U(\Sigma_r^-, R) \cap \E(\Phi, R, I) = \U(\Sigma_r^-, I)$ we get that:
\begin{equation*} \label{rel:ninv} A^{X_{-\alpha\ssub{r}}(R)} = \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot B ^{X_{-\alpha\ssub{r}}(R)} \cdot \EP_s(R, I) = A, \end{equation*}
which implies the assertion of the lemma. \end{proof}

@@

Yet another advantage of weight diagrams is that they allow one to visualize the action of elementary root unipotents $x_\alpha(\xi)$ on $v = \sum_{\lambda \in \Lambda(\pi)} v_\lambda e_\lambda \in V$ described in \cref{lemma:Matsumoto}.
Such description for microweight $\pi$ and $\alpha = \pm\alpha_i\in \pm\Pi$ is particularly simple: 
for every bond of the diagram joining vertices $\lambda$ and $\lambda + \alpha$ the element $x_{\alpha}(\xi)$ adds $\pm \xi \cdot v_\lambda$ to $v_{\lambda+\alpha}$.
See~\cite[Section~3.4]{PSV98} for more detailed description.

\begin{figure}
\[\begin{array}{l @{\qquad} l @{\qquad} c @{\quad} c @{\qquad} l @{\qquad} l}
\Phi                                 & (s,r)         & |\Lambda(\pi)| & \text{type of $\pi$} & |\Lambda(\pi')|& |\Gamma|  \\ \hline\vphantom{\Bigl(}
\rA_\ell,\ \ell\geqslant 2           & (1,\ell)      & \ell+1         & \text{natural}       & \ell           & 1  \\     
\rB_\ell,\ \ell\geqslant 2           & (1,\ell)      & 2\ell+1        & \text{natural}       & \ell           & 1  \\     
\rC_\ell,\ \ell\geqslant 2           & (1,\ell)      & 2\ell          & \text{natural}       & \ell           & 1  \\
\rD_\ell,\ \ell\geqslant 4           & (1,\ell)      & 2\ell          & \text{natural}       & \ell           & 2  \\ 
\rD_\ell,\ \ell\geqslant 4           & (\ell,\ell-1) & 2^{\ell-1}     & \text{half-spinor}   & \ell           & \ell-2  \\
\rE_\ell,\ \ell=6,7                  & (\ell,2)      & 27, 56         & \text{minimal}       & \ell           & 3       \\ 
\rE_\ell,\ \ell=6,7                  & (\ell,1)      & 27, 56         & \text{minimal}       & 2(\ell-1)      & \ell-1  \end{array}\]
 \caption[Table]{List of representation involved in the proof of \cref{thm:DennisVaserstein}.} \label{fig:table}
\end{figure}

Now let $B$ be the set of all elements $g$ of $\E(\Delta_r,R, I)$ such that $(g \cdot v^+)_\lambda = 0$ for all $\lambda\in\Gamma$.
Applying \cref{lemma:uraction} to the subsystem $\Delta_r$ we find
$x\in\U(\Delta_r^+, I)$, $y\in \U(\Delta_r^-, I)$ such that $yx\cdot g \in B$.
This proves the first assumption of \cref{lemma:Stein_reduction}, indeed:
\[ \U(\Sigma^+_r, I) \cdot \U(\Sigma^-_r, I) \cdot g = \U(\Sigma^+_r, I) x^{-1} \cdot \U(\Sigma^-_r, I)^{x^{-1}} y^{-1} (yxg) \subseteq \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot B. \]
To prove the second assumption of \cref{lemma:Stein_reduction} notice that by \cref{lemma:Matsumoto} and the definition of $\Gamma$ for any $s\in I$, $ g\in B$ one has $x_{-\alpha_r}(s) \cdot g \cdot v^+ = g \cdot v^+$ hence
\[ X_{-\alpha\ssub{r}}(I)^{B} \subseteq \U(\Phi^-, I) \cap \Stab(v^+) \subseteq \U(\Delta_s^-, I) \subseteq \EP_s(R, I). \]

\begin{proof}[Proof of \cref{thm:DennisVaserstein}]
By the above discussion we may assume that the assertion of \cref{lemma:Stein_reduction} holds.
Set $\Pi' = \Pi \setminus \{\alpha_s\}$.
From \cref{lemma:dv-normal} and \cref{lemma:Stein_reduction} it follows that $X_\alpha(R) \subseteq N_{rs}$ for $\alpha \in \Pi' \cup -\Pi'$.
Since $\Delta_s$ is irreducible we get from \cref{item-egen} that $\E(\Delta_s, R) \subseteq N_{rs}$.

Our next step is to show that $\U(\Sigma_s, R) \subseteq N_{rs}$.
First of all, notice that by \cref{lemma:dv-normal} we have the inclusion $X_{\alpha_s}(R) \subseteq N_{rs}$.
In all cases under consideration except $\Phi=\rC_\ell$ we have $m_s(\alpha_{\mathrm{max}})=1$.
Therefore, for $\Phi\neq \rB_\ell, \rC_\ell$ all the roots of $\Sigma^+_s$ have the same $s$-shape and length and the assertion follows from \cref{item-trans2}.

@@

We defer the proof in the case $\Phi=\rC_\ell$ until we prove \cref{lemma:DVcaseCl} below.

Our ultimate goal is to show the inclusion $\E(\Phi, R, I) \subseteq L_{rs}$. 
By \cref{prop:Stepanov} it is enough to prove that $\mathcal{Z}(\Sigma^-_s) \subseteq L_{rs}$.
In view of formula~\eqref{rel:NnormL} and the previous part of the proof it suffices to show only that $\mathcal{X} \subseteq L_{rs}$.
It is clear that $\EP_r(R, I) \subseteq L_{rs}$.
Since $\EP_s(R, I) \subseteq \EP_s(R) \subseteq N_{rs}$ we also conclude that $\EP_s(R, I) \subseteq L_{rs}$, indeed, for $g \in \EP_s(R,I)$ one has
\[ g \cdot A_{rs} \subseteq g \cdot {A_{rs}}^g = A_{rs} \cdot g = A_{rs}. \]
Thus, we are left to prove the inclusion $\U(\Sigma^-_r \cap \Sigma^-_s, I) \subseteq L_{rs}$.

Just as in the above argument all the cases except $\Phi = \rB_\ell, \rC_\ell$ follow from \cref{item-trans2}.
In the case $\Phi=\rB_\ell$ from $x_{0, 1}(-a) = [x_{2,1}(-a), x_{0, 2}(-1)]\cdot x_{-2,1}(a)$ we conclude that
$$X_{0,1}(I) \subseteq X_{2,1}(I) \cdot X_{2,1}(I)^{x_{0,2}(1)} \cdot X_{-2,1}(I) \subseteq L_{rs} \cdot L_{rs}^{N_{rs}} \cdot L_{rs} \subseteq L_{rs},$$
whence the statement of the theorem follows. \end{proof}

@@

By \cref{item:asrUnipC} (applied to the subgroup $\G(\Delta_1, R, I)$) we find for every $g \in \EP_1(R, I)$ a matrix $x \in \U(\Sigma_\ell \cap \Delta_1, I)$ such that $xg \in C$.  
Notice that one immediately gets the equality $A_{\ell, 1} = A'$ from this.
Indeed for $g\in \EP_1(R, I)$ one has
\begin{equation*} \EP_\ell(R, I) \cdot \U(\Sigma_1^- \cap \Sigma_\ell^-, I) \cdot g \subseteq 
 \EP_\ell(R, I)x^{-1}  \cdot \U(\Sigma_1^-, I) \cdot xg \subseteq A'. \end{equation*}

By the very definition of $C$, for every $g \in C$ one can choose $y \in \U(\Sigma_1 \cap \Delta_\ell, I)$ such that $(y \cdot g)_{1,2} = 0$.
Consequently, for every $g\in C$ one has
\begin{multline*}
 \EP_\ell(R, I) \cdot \U(\Sigma_1^- \cap \Sigma_\ell^-, I) \cdot g \subseteq \EP_\ell(R, I) y^{-1} \cdot \U(\Sigma_\ell^-\cap \Sigma_1^-, I)^{y^{-1}} \cdot y g \subseteq \\
  \subseteq \EP_\ell(R, I) \cdot \U(\Sigma_\ell^-, I) \cdot y g
\end{multline*}
Direct calculation using \cref{lemma:Chevalley-Matsumoto} shows that $(yg)^{x_{2,1}(\xi)} = u h$ for $\xi \in R$, $u \in \U(\Sigma_1^-, I)$, $h \in \EP_1(R, I)$ hence
\begin{multline*} {A_{\ell,1}}^{X_{-\alpha_1}(R)} = A'^{X_{2,1}(R)} \subseteq \EP_\ell(R, I)^{X_{2,1}(R)} \cdot \U(\Sigma_\ell^-, I)^{X_{2,1}(R)} \cdot \U(\Sigma_1^-, I) \cdot \EP_1(R, I) \subseteq \\
 \subseteq \EP_\ell(R, I) \cdot \U(\Phi^-, I) \cdot \EP_1(R, I) \subseteq A_{\ell,1} \end{multline*}
 as claimed.
\end{proof}

\begin{proof}[End of the proof of \cref{thm:DennisVaserstein}]
In the remaining case $\Phi=\rC_\ell$ we conclude from \cref{lemma:dv-normal,lemma:Stein_reduction,lemma:DVcaseCl} that $X_{\pm \alpha_i}(R) \subseteq N_{\ell,1}$, $1\leq i\leq \ell$.
Therefore, by \cref{lemma:weylfacts} we get that $\widetilde{W}(\Phi) \subseteq N_{\ell,1}$ and hence $\mathcal{X} \subseteq L_{\ell,1}$ as required.
\end{proof}

### 2015-09-10 paper.tex
Minor
Examples styled as remarks
Minor changes

%Theorem counters
\newlist{thmlist}{enumerate}{1} \setlist[thmlist]{label=(\roman{thmlisti}), ref=\thethm.(\roman{thmlisti}),noitemsep} \Crefname{thmlisti}{Theorem}{Theorems}
\newlist{lemlist}{enumerate}{1} \setlist[lemlist]{label=(\roman{lemlisti}), ref=\thelemma.(\roman{lemlisti}),noitemsep} \Crefname{lemlisti}{Lemma}{Lemmas}

@@

\newtheorem{lemma}{Lemma} \numberwithin{lemma}{section} \Crefname{lemma}{Lemma}{Lemmas}
\newtheorem{cor}[lemma]{Corollary} \Crefname{cor}{Corollary}{Corollaries}
\newtheorem{prop}[lemma]{Proposition} \Crefname{prop}{Proposition}{Propositions}
\newtheorem{example}[lemma]{Example} \Crefname{example}{Example}{Examples}
\theoremstyle{definition} \newtheorem{dfn}[lemma]{Definition} \Crefname{dfn}{Definition}{Definitions}
\theoremstyle{remark} \newtheorem{rem}[lemma]{Remark} \Crefname{rem}{Remark}{Remarks}

\newtheorem*{thm*}{Theorem}
\newtheorem*{lemma*}{Lemma}

@@

On the other hand, much less is known about the width of the relative group $\G(\Phi, R, I)$. 
Set $z_\alpha(s, \xi) = x_{\alpha}(s)^{x_{-\alpha}(\xi)}$, $s\in I$, $\xi\in R$.
It is a classical result of J.~Tits and L.~Vaserstein (see e.\,g.~\cite[Theorem~2]{Va86}) that the relative elementary group $\E(\Phi, R, I)$ is generated by
the set of elements $\mathcal{Z} = \{ z_\alpha(s,\xi) \mid \alpha \in \Phi,\ s\in I,\ \xi \in R \}.$

@@

The same argument combined with~\cref{lemma:abs} also proves the third statement. Indeed, by our assumption all roots of the same length lying in $\Sigma_s$ have the same $s$-shape.

@@

\subsection{Relative Chevalley groups}\label{sec:relative-elementary}
Let $I\leq R$ be an ideal. Denote by $\E(\Phi, I)$ the subgroup of $\G_{sc}(\Phi, R)$ generated by the elementary root unipotents $x_\alpha(\xi)$, $\alpha\in\Phi$, $\xi\in I$.

We denote by $\E(\Phi, R, I)$ the normal closure of $\E(\Phi, I)$ in $\E(\Phi, R)$, in other words $\E(\Phi, R, I) = \E(\Phi, I)^{\E(\Phi, R)}$.
Recall from the introduction that the elements $z_\alpha(s, \xi) = x_\alpha(s)^{x\ssub{-\alpha}(\xi)}$ generate $\E(\Phi, R, I)$ as an abstract group.

>>>>

\newlist{thmlist}{enumerate}{1} \setlist[thmlist]{label=(\roman{thmlisti}), ref=\thethm.(\roman{thmlisti}),noitemsep} \Crefname{thmlisti}{Theorem}{Theorems}
\newlist{lemlist}{enumerate}{1} \setlist[lemlist]{label=(\roman{lemlisti}), ref=\thelemma.(\roman{lemlisti}),noitemsep} \Crefname{lemlisti}{Lemma}{Lemmas}

@@

\newtheorem{lemma}{Lemma} \numberwithin{lemma}{section} \Crefname{lemma}{Lemma}{Lemmas}
\newtheorem{cor}[lemma]{Corollary} \Crefname{cor}{Corollary}{Corollaries}
\newtheorem{prop}[lemma]{Proposition} \Crefname{prop}{Proposition}{Propositions}
\newtheorem*{thm*}{Theorem}
\newtheorem*{lemma*}{Lemma}
\theoremstyle{definition} \newtheorem{dfn}[lemma]{Definition} \Crefname{dfn}{Definition}{Definitions}
\newtheorem{example}[lemma]{Example} \Crefname{example}{Example}{Examples}
\theoremstyle{remark} \newtheorem{rem}[lemma]{Remark} \Crefname{rem}{Remark}{Remarks}

@@

On the other hand, much less is known about the width of the relative group $\G(\Phi, R, I)$ and the relative elementary group $\E(\Phi, R, I)$.
Recall that the \emph{relative elementary group} $\E(\Phi, R, I)$ is defined as the normal closure of $\E(\Phi, I)$ in $\E(\Phi, R)$, where
$\E(\Phi, I)$ denotes the subgroup of $\G_{sc}(\Phi, R)$ generated by all elementary root unipotents $x_\alpha(\xi)$, $\alpha\in\Phi$, $\xi\in I$, i.\,e. $\E(\Phi, R, I) = \E(\Phi, I)^{\E(\Phi, R)}$.

Set $z_\alpha(s, \xi) = x_{\alpha}(s)^{x_{-\alpha}(\xi)}$, $s\in I$, $\xi\in R$.
It is a classical result of J.~Tits and L.~Vaserstein (see e.\,g.~\cite[Theorem~2]{Va86}) that the relative elementary group $\E(\Phi, R, I)$ is generated by
the set of elements $\mathcal{Z} = \{ z_\alpha(s,\xi) \mid \alpha \in \Phi,\ s\in I,\ \xi \in R \}.$

@@

The same argument combined with \cref{lemma:abs} also proves the third statement. Indeed, by our assumption all roots of the same length lying in $\Sigma_s$ have the same $s$-shape.

@@

\subsection{Relative Chevalley groups}\label{sec:relative-elementary}
Recall from the introduction that the elements $z_\alpha(s, \xi) = x_\alpha(s)^{x\ssub{-\alpha}(\xi)}$ generate $\E(\Phi, R, I)$ as an abstract group.
